Automated Topic Naming

### 2011-09-05 ese/ese.tex
migod's changes

Topic modeling is a machine learning technique which creates
multinomial distributions of words extracted from a text corpus. 
This technique infers the hidden structure of a corpus using posterior
inference: the probability of the hidden structure given the data. 
Topic models are useful in software maintenance because they summarize
the key concepts in a corpus, such as source code, commit comments, or
mailing-list messages, by identifying statistically co-occurring words. 
Among other uses, it can quickly give developers an overview of where significant
activity has occurred, and gives managers or maintainers a sense of
project history. 
%A major challenge for topic modeling is to accurately identify the
%summary label for a topic; in the previous case, perhaps
%\emph{``event-handling''} would be appropriate. 
%Current approaches are manual: they rely on human expertise to
%recognize the appropriate label. 
%Furthermore, to date the results of topic modeling are project
%specific, and not generalizable. 
%This paper presents an approach, \emph{labelled topic extraction}, which addresses these two problems.

@@

%We first introduces labelled topic extraction, and then uses that technique to analyze development activity in two large-scale examples.
We begin by discussing related work in Section \ref{sec:related}.
Next, we describe how we generated our data (Section \ref{sec:wordlist}). For semi-unsupervised classification (Section \ref{sec:unsuplabelling}), we
begin by creating word-lists to signify when a topic matches an NFR label. We then apply our classifier and analyze the results. 
%and how we created the word-lists used in unsupervised classification. 
%We show that labels with their topics can be learned and used to classify other data-sets, either without training 
%Our goal is to label a given topic with either an NFR from our taxonomy,
 %Section \ref{sec:unsuplabelling} presents our technique for using word-lists to do unsupervised classification, and describes the results.
In Section \ref{sec:suplabelling}, we manually annotate the topics, and use those annotations as training data for supervised classification.  
%We then present visualizations of named topics and their trends over time to aid communication and analysis. 
To demonstrate an application of labelled topic extraction, we use an exploratory case study of two open source database systems to show how named
topics can be compared between projects  (Section \ref{sec:analysis}). 
The paper concludes with a discussion of limitations (Section \ref{sec:limit}), and future work.

@@

Cleland-Huang and her colleagues have investigated mining requirements documents for non-functional requirements (NFR) (quality
requirements)~\cite{Cleland-Huang2006}. 
Their approach is similar to ours, as they mined keywords from NFR
catalogues.
They differ because they mine requirements documents where as we mine revisions.
%One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. 
They demonstrated a recall of $80\%$ with precision of $57\%$ for the \emph{security} NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our research differs because we use a more comprehensive set of terms based on the taxonomy we chose.
Another difference is that we make cross-project comparisons instead of focusing
on a single project.
%They relied on requirements documents instead of version control
%histories that we use.
%The objective of Cleland-Huang's study was to identify new NFRs for system development, 
%yet our objective was to recover those latent NFRs from commit-log messages of the project.

@@

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero, one, or more NFRs. 
For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement
in the source code that related to \textit{usability}. 
However, traditional machine learning techniques, such as Naive Bayes, can only map topics to a single class. 
tab:iterrThe Mulan~\cite{mulan} library encapsulates several different multi-label machine learners which can label elements with multiple labels.
Mulan also includes methods for determining the performance of such techniques.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank
% multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has~\cite{aranda09icse}. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why}  because they show reasons why changes
occurred rather than \emph{how}. 
The \emph{how} of a change is the change itself, the purpose or
\emph{why} is what we are after.
We investigate the history of the two large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.

\item \emph{Do projects differ in their relative interest in NFRs?} A
  project manager, especially a systems-manager, would be interested
  in knowing whether a particular NFR, such as \emph{reliability}, was
  more important for one project than another. This could be to
  confirm the initial design goals, or to track the progress on that
  quarter's objectives.  The difference in NFR proportion is
  interesting because it implies a difference in focus between two projects.

\item \emph{Do different developers work on different NFRs?} For a given project, it is reasonable to think that developers are either assigned
(in commercial organizations) or choose (in open-source organizations) to a particular NFR. For example, one developer might be more junior, and take
responsibility for the low-impact reliability fixes. Another, more senior developer might assume responsibility for major improvements such as efficiency
improvements.

@@

Our theory is that the less frequent committers perhaps are more
focused and less general, thus their distributions of topics are
different than the main developers who commit code in many different
contexts. Perhaps the lead developers ``wear more hats'' or have more
time to ``wear more hats''.

@@

Authors Neil and Abram each annotated the PostgreSQL topics in order
to determine inter-rater reliability. While when they read each others
annotations they generally agreed, the inter-rater reliability did not
bear this out.

@@

After some discussion we concluded that usability was a source of
disagreement. Do user manuals improve usability? Is a command-line
option a usability issue? These kinds of questions illustrate some of
the agreement, disagreement and ambiguity about these labels. Further
more, both annotators found that the annotation was time-consuming and
difficult.

@@

\section{Conclusions}
This paper presented a cross-project data mining technique,
\emph{labelled topic extraction}. %The technique leveraged a
%non-functional requirements (NFRs) taxonomy to mine and label latent
%software development topics. 
Previous topic analysis research produced project-specific
topics that needed to be manually labelled.
%, but topics without labels
%are difficult to interpret, and manually labelling them is
%costly. Furthermore, previous work was project-specific and thus incomparable. 
To improve on this, we leveraged software engineering standards,
specifically the ISO9126 quality taxonomy, to produce a method of partially-automated (supervised) and fully-automated (semi-unsupervised) topic labelling.
Since the word-list technique is not project-specific, we used it to compare two distinct projects, where we showed our technique produced interesting
insight into maintenance activity. %topics and artifacts from project histories.
% Our contributions include:
% \begin{itemize}
% \item We provided an unsupervised method of topic labelling (word-lists);
% %\item Our unsupervised method can be applied to projects without training;
% \item We demonstrated a supervised method of labelling topics by a single NFRs (machine learning);
% \item We demonstrated a supervised method of labelling topics by multiple NFRs (multi-label machine learning);
% \item We provided a method of cross-project analysis via topic labelling;
% \item We demonstrated a method of visualizing these topics across time, which we used to analyze maintenance activities.
% \end{itemize}

>>>>

Topic modeling is a machine learning technique that creates
multinomial distributions of words extracted from a text corpus. 
This technique infers the hidden structure of a corpus using posterior
inference: the probability of the hidden structure given the data. 
Topic models are useful in software maintenance because they summarize
the key concepts in a corpus, such as source code, commit comments, or
mailing-list messages, by identifying statistically co-occurring words. 
Among other uses, it can quickly give developers an overview of where significant
activity has occurred, and gives managers or maintainers a sense of
project history. 
%A major challenge for topic modeling is to accurately identify the
%summary label for a topic; in the previous case, perhaps
%\emph{``event-handling''} would be appropriate. 
%Current approaches are manual: they rely on human expertise to
%recognize the appropriate label. 
%Furthermore, to date the results of topic modeling are project
%specific, and not generalizable. 
%This paper presents an approach, \emph{labelled topic extraction}, which addresses these two problems.

@@

%We first introduces labelled topic extraction, and then uses that technique to analyze development activity in two large-scale examples.
We begin by discussing related work in Section \ref{sec:related}.
Next, we describe how we generated our data (Section \ref{sec:wordlist}). For semi-unsupervised classification (Section \ref{sec:unsuplabelling}), we
begin by creating word-lists to signify when a topic matches an NFR label. We then apply our classifier and analyze the results. 
%and how we created the word-lists used in unsupervised classification. 
%We show that labels with their topics can be learned and used to classify other data-sets, either without training 
%Our goal is to label a given topic with either an NFR from our taxonomy,
 %Section \ref{sec:unsuplabelling} presents our technique for using word-lists to do unsupervised classification, and describes the results.
In Section \ref{sec:suplabelling}, we manually annotate the topics, and use those annotations as training data for supervised classification.  
%We then present visualizations of named topics and their trends over time to aid communication and analysis. 
To demonstrate an application of labelled topic extraction, we use an exploratory case study of three open source database systems to show how named
topics can be compared between projects  (Section \ref{sec:analysis}). 
The paper concludes with a discussion of limitations (Section \ref{sec:limit}), and future work.

@@

Cleland-Huang and her colleagues have investigated mining requirements
documents for non-functional requirements (NFR) (software
qualities)~\cite{Cleland-Huang2006}.  Their approach is similar to
ours, as they mined keywords from NFR catalogues.  They differ because
they mine requirements documents where as we mine revisions.
%One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. 
They demonstrated a recall of $80\%$ with precision of $57\%$ for the \emph{security} NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our research differs because we use a more comprehensive set of terms based on the taxonomy we chose.
Another difference is that we make cross-project comparisons instead of focusing
on a single project.
%They relied on requirements documents instead of version control
%histories that we use.
%The objective of Cleland-Huang's study was to identify new NFRs for system development, 
%yet our objective was to recover those latent NFRs from commit-log messages of the project.

@@

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero, one, or more NFRs. 
For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement
in the source code that related to \textit{usability}. 
However, traditional machine learning techniques, such as Naive Bayes, can only map topics to a single class. 
The Mulan~\cite{mulan} library encapsulates several different multi-label machine learners which can label elements with multiple labels.
Mulan also includes methods for determining the performance of such techniques.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank
% multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has~\cite{aranda09icse}. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why}  because they show reasons why changes
occurred rather than \emph{how}. 
The \emph{how} of a change is the change itself, the purpose or
\emph{why} is what we are after.
We investigate the history of the three large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.

\item \emph{Do projects differ in their relative interest in NFRs?} A
  project manager, especially a systems-manager, would be interested
  in knowing whether a particular NFR, such as \emph{reliability}, was
  more important for one project than another. This could be to
  confirm the initial design goals, or to track the progress on that
  quarter's objectives.  The difference in NFR proportion is
  interesting because it implies a difference in focus between projects.

\item \emph{Do different developers work on different NFRs?} For a given project, it is reasonable to think that developers are either assigned
(in commercial organizations) or choose (in open-source organizations) to work on a particular NFR. For example, one developer might be more junior, and take
responsibility for the low-impact reliability fixes. Another, more senior developer might assume responsibility for major improvements such as efficiency
improvements.

@@

Our theory is that the less frequent committers are more
focused and less general, thus their distributions of topics are
different than the main developers who commit code in many different
contexts.  The lead developers either ``wear more hats'' or have more
time to ``wear more hats''.

@@

To determine inter-rater reliability two of the authors---Ernst and Hindle---each annotated the PostgreSQL topics,
and then evaluated each other's annotations.

@@

After some discussion we concluded that usability was a source of
disagreement. Do user manuals improve usability? Is a command-line
option a usability issue? These kinds of questions illustrate some of
the agreement, disagreement and ambiguity about these labels. Furthermore, 
both annotators found that the annotation was time-consuming and
difficult.

@@

\section{Conclusions}
This paper presented a cross-project data mining technique,
\emph{labelled topic extraction}. %The technique leveraged a
%non-functional requirements (NFRs) taxonomy to mine and label latent
%software development topics. 
Previous topic analysis research produced project-specific
topics that needed to be manually labelled.
%, but topics without labels
%are difficult to interpret, and manually labelling them is
%costly. Furthermore, previous work was project-specific and thus incomparable. 
To improve on this, we leveraged software engineering standards,
specifically the ISO9126 quality taxonomy, to produce a method of partially-automated (supervised) and fully-automated (semi-unsupervised) topic labelling.
Since the word-list technique is not project-specific, we used it to compare three distinct projects, where we showed our technique produced interesting
insight into maintenance activity. %topics and artifacts from project histories.
% Our contributions include:
% \begin{itemize}
% \item We provided an unsupervised method of topic labelling (word-lists);
% %\item Our unsupervised method can be applied to projects without training;
% \item We demonstrated a supervised method of labelling topics by a single NFRs (machine learning);
% \item We demonstrated a supervised method of labelling topics by multiple NFRs (multi-label machine learning);
% \item We provided a method of cross-project analysis via topic labelling;
% \item We demonstrated a method of visualizing these topics across time, which we used to analyze maintenance activities.
% \end{itemize}
